---
title: 'TSA Screening Risk Analysis & Incident Rate Assessment'
author: "SAKINA SARFRAZ"
date: "December 14, 2025"
output:
  html_document:
    toc: true
    theme: united
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
library(tidyverse) 
library(dplyr)
library(stringr)
library(maps)
library(lubridate)
library(dslabs)
library(tidyr)
library(readxl)
library(haven)
library(weights)
library(scales)

```


## Project Context

This analysis was originally completed as a final exam project for DATA 2100 
(Introduction to Data Analytics) at the University of Pennsylvania. The project 
has been adapted and expanded with a security analytics framework to demonstrate 
skills applicable to threat detection and security operations.

**Original Assignment:** Analyze TSA checkpoint and firearm confiscation data 
to identify patterns and insights.

**Security-Focused Extension:** Reframed analysis to focus on anomaly detection, 
risk assessment, and threat pattern identification - core skills for Security 
Operations Center (SOC) analysts.




## Analysis Questions

The following analysis answers specific investigative questions using 2.7M+ 
TSA checkpoint records from 2022.


## Question #A TSA Checkin & Firearm Confiscations 

## Question #1

1. Load in the TSA checkpoint data from Jan 2 through Jan 8 (tsa_2022-01-02_2022-01-08). How many
people went through the Terminal B checkpoint at the Philadelphia International Airport (PHL) at 8
AM on January 5, 2022?

```{R}

unzip("tsa.zip")

tsa <- read.csv("tsa/tsa_2022-01-02_2022-01-08.csv")

#names(tsa)

#unique(tsa$airport)
#unique(tsa$checkpoint_name)
#unique(tsa$date)
#unique(tsa$hour)
#unique(tsa$checkpoint_name[tsa$airport == "Philadelphia International"])


result <- tsa[tsa$airport == "Philadelphia International" &
  tsa$checkpoint_name == "Checkpoint B" &
  tsa$date == "2022-01-05" &
  tsa$hour == "08:00", ]

result$checkins


```
486 people went through the Terminal B checkpoint at the Philadelphia International Airport (PHL) at 8
AM on January 5, 2022.

## Question #2

2. Write a loop that loads in all of the TSA checkpoint data from 2022 and creates on single dataset.
Report out dimensions of this new dataset.

```{R}



unzip("tsa.zip", exdir = "tsa")

files <- list.files("tsa", pattern = "\\.csv$", full.names = TRUE)


tsa_2022 <- data.frame()


for (file in files) {
  temp <- read.csv(file, stringsAsFactors = FALSE)
  tsa_2022 <- rbind(tsa_2022, temp)
}


dim(tsa_2022)


```
The dimensions of this new dataset has 2,708,662 observations and 12 variables.

## Question #3

3. Subset the checkpoint data to include only Philadelphia International (PHL). Aggregate this data to
determine the number of people who went through each Philly checkpoint daily.

```{R} 


phl_data <- tsa_2022[tsa_2022$airport == "Philadelphia International", ]


phl_data$checkins <- as.numeric(phl_data$checkins)


phl_daily <- aggregate(checkins ~ checkpoint_name + date, data = phl_data, sum)


head(phl_daily)



``` 



## Question #4

4. Graph the amount of people traveling through each Philly checkpoint every day in 2022. Describe
what you learned from your graph.
  
```{R} 


phl_daily$date <- as.Date(phl_daily$date)


ggplot(phl_daily, aes(x = date, y = checkins, color = checkpoint_name)) +
  geom_line(size = 1) +
  geom_point(size = 1.5) +
  labs(title = "Daily TSA Checkins at Philadelphia International (2022)",
    x = "Month",
    y = "Number of Passengers",
    color = "Checkpoint") +
  scale_x_date(date_breaks = "1 month",            
    date_labels = "%b") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom")

``` 
The graph of daily check-ins at Philadelphia International Airport in 2022 shows that passenger traffic is concentrated at certain checkpoints. Checkpoint D/E consistently handles the most passengers throughout the year, making it the busiest, followed by Checkpoint B, A East, Checkpoint C, A West Sec 7, and then Checkpoint F. This hierarchy of checkpoint usage remains stable over time suggesting a consistent distribution of passengers. Since D/E and B handle the most passengers, airport management may need more staff, lanes, or resources at these locations, while smaller checkpoints require less.



## Question #5

5. To help assist us with booking flights in the future, we want to create a function that identifies the
time of day when an airport is on average the busiest. The goal is to create a single function where you
can plug in an airports call letters and the output is the time of day when it is the busiest. Use your
newly created function to report out the busiest time to checkin at the New York City area airports:
Newark (EWR), John F Kennedy (JFK) and LaGuardia (LGA).

```{R}

tsa_2022$checkins <- as.numeric(tsa_2022$checkins)


busiest_hour <- function(airport_code) {
  
  airport_data <- tsa_2022[tsa_2022$call_letters == airport_code, ]
  
  
  avg_by_hour <- aggregate(checkins ~ hour, data = airport_data, FUN = mean)
  
  
  busiest <- avg_by_hour[which.max(avg_by_hour$checkins), "hour"]
  
  return(busiest)
}

busiest_hour("EWR")  # Newark
busiest_hour("JFK")  # John F Kennedy
busiest_hour("LGA")  # LaGuardia




```
The busiest times to check in at the New York City area airports are:
Newark (EWR): 16:00 or 4:00 p.m
John F Kennedy (JFK): 17:00 or 5:00 p.m
LaGuardia (LGA): 09:00 or 9:00 a.m



## Question #6

6. Load in the firearm confiscation data. Which airport confiscated the most firearms in 2022? How many
did they confiscate?

```{R}


tsa_guns_2022 <- read.csv("tsa_guns_2022.csv", stringsAsFactors = FALSE)

#names(tsa_guns_2022)



total_firearms <- aggregate(date ~ airport, data = tsa_guns_2022, FUN = length)
names(total_firearms)[2] <- "num_firearms"

max_idx <- which.max(total_firearms$num_firearms)
busiest_airport <- total_firearms$airport[max_idx]
num_confiscated <- total_firearms$num_firearms[max_idx]


busiest_airport
num_confiscated



```
Hartsfield–Jackson Atlanta International Airport (ATL) confiscated the most firearms in 2022, with 448 total confiscations.



## Question #7

7. Let’s check which airport has the most guns confiscated relative to the number of people who actually
go through the check points. To do this, aggregate both the TSA checkin data and the firearm data
to get an annual measurement by airport. Merge the datasets together. If there were no confiscations
at an airport, make sure this is recorded as a zero. Create a new confiscation rate variable. Out of the
airports that confiscated more than 10 guns, which airport had the highest confiscation rate?

```{R}


tsa_annual <- aggregate(checkins ~ call_letters,
  data = tsa_2022,sum)

names(tsa_annual) <- c("airport", "checkins")


guns_annual <- aggregate(date ~ airport,
  data = tsa_guns_2022,
  FUN = length)

names(guns_annual) <- c("airport", "firearms")


combined <- merge(tsa_annual,
  guns_annual,
  by = "airport",
  all.x = TRUE)

combined$firearms[is.na(combined$firearms)] <- 0

combined$confiscation_rate <- combined$firearms / combined$checkins

over_10 <- combined[combined$firearms > 10, ]

highest_rate_airport <- over_10[
  which.max(over_10$confiscation_rate),
]

highest_rate_airport


```

Out of the airports that confiscated more than 10 guns, Orlando International Airport (MCO) had the highest confiscation rate of 7.34.



## Question #8

8. Create a graph that plots the number of confiscations by the number of travelers for the airports that
confiscated more than 10 guns in 2022. Which airports standout?

```{R}

over_10 <- combined[combined$firearms > 10, ]


ggplot(over_10, aes(x = checkins, y = firearms, label = airport)) +
  geom_point(color = "steelblue", size = 2, alpha = 0.5) +      
  geom_text(nudge_y = 0.5, size = 3, check_overlap = TRUE) +  
  scale_x_continuous(labels = scales::comma) +    
  scale_y_continuous(labels = scales::comma) +     
  labs(title = "TSA Firearm Confiscations vs Travelers (Airports with >10 Guns in 2022)",
    x = "Number of Travelers",
    y = "Number of Firearms Confiscated") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(angle = 0))



ggsave("visualizations/checkpoint_traffic.png", 
       plot = last_plot(), 
       width = 10, 
       height = 6, 
       dpi = 300,
       create.dir = TRUE)

ggsave("visualizations/firearm_confiscations.png",
       plot = last_plot(),
       width = 10, 
       height = 6,
       dpi = 300,
       create.dir = TRUE)

#combined[combined$airport == "ATL", ]

```

The airports that stand out in 2022 for firearm confiscations relative to the number of travelers are ATL, DFW, LAX, and MIA. ATL had over 400 firearms confiscated with approximately 12,000 travelers, making it a clear outlier with a high confiscation rate. DFW also had a high number of confiscations, around 380, with roughly 22,000 passengers. On the other hand, LAX and MIA had fewer firearms confiscated, under 100 each, but a much higher number of travelers, around 23,000–24,000, which makes them notable for having a low confiscation rate relative to volume. Overall, these airports stand out because their confiscation numbers are disproportionately high or low compared to the general trend of firearms versus traveler counts at other airports.




## Appendix: All code used to make this document 

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```



